A Formal Model of Checked C

### 2022-12-13 sandp23/background.tex
Adding back

>>>>

\noindent
\myparagraph{Ensuring Spatial Memory Safety}
The \checkedc compiler will instrument loads and stores of checked
pointers to confirm the pointer is non-null, and additionally for $\arr$ and $\ntarr$ pointers the access is within
the specified bounds.
For instance, in the code \inlinecode{if (n>0) a[n-1] =} $...$ the write
is via address $\alpha = \inlinecode{a + sizeof(int)}\!\times\!\code{(n-1)}$. If the
bounds of \code{a} are \code{count(u)}, the
inserted check will confirm that prior to dereference
$\inlinecode{a} \leq \alpha < \inlinecode{a + sizeof(int)} \!\times\!
\inlinecode{u}$.
Failed checks throw an exception.

Oftentimes, inserted checks can be optimized away by LLVM.
Consider the above code to be enclosed in another condition, such as,~\inlinecode{if (n<u) if (n>0) a[n-1] =}.
In such cases, the inserted check can be
removed as the outer condition $\inlinecode{n<u}$ already ensures that the
dereference is within bounds.
Dual~\etal~\cite{duanrefactoring} found essentially no
overhead when running Checked C-converted portions of the FreeBSD kernel.

\noindent
\myparagraph{Backward Compatibility}
